\documentclass[a4paper,10pt]{article}
\usepackage{graphicx}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{helvet}
\usepackage{xcolor}

\geometry{left=0.75in, right=0.75in, top=0.75in, bottom=0.75in}
\renewcommand{\familydefault}{\sfdefault}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
}

% Title formatting
\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}
\titlespacing*{\section}{0pt}{*1}{*1}

% Color definitions for Material Design
\definecolor{primary}{RGB}{33, 150, 243}
\definecolor{secondary}{RGB}{255, 87, 34}
\definecolor{text}{RGB}{33, 33, 33}

\begin{document}

\begin{center}
    \textbf{\huge Cameron Aaron} \\
    Greater Seattle Area \\
    \href{mailto:cameronaaron1@gmail.com}{cameronaaron1@gmail.com} \\
    818-385-7117 \\
    \href{https://linkedin.com/in/kamisama}{linkedin.com/in/kamisama}
\end{center}

\section*{Summary}
\color{text}
I am passionate about advancing education and research at the intersection of AI and cognitive neuroscience. With experience at leading companies such as Dutchie, GitHub, SpaceX, and Microsoft, I deliver high-quality products and services. I hold a double major in Computer Science and Psychology, a minor in Cognitive Science, and a Certificate of Arts and Technology from Connecticut College.

\section*{Skills}
\begin{itemize}[leftmargin=0cm, itemsep=0pt, label={}]
    \item \textbf{Programming:} Python, C++, JavaScript, SQL
    \item \textbf{Frameworks:} React.js, Node.js, Django
    \item \textbf{Technologies:} AWS, Azure, GCP, Docker, Kubernetes
    \item \textbf{Databases:} MySQL, PostgreSQL, MongoDB
    \item \textbf{Other:} DevOps, Cloud Migrations, UX/UI Design, Data Analysis
\end{itemize}

\section*{Experience}
\begin{itemize}[leftmargin=0cm, itemsep=0pt]
    \item \textbf{Director of IT, Biopsychology \& Engineering Instructor, Bridges Academy}
        \hfill \textit{Nov 2022 – Present}
        \begin{itemize}[leftmargin=0.5cm, itemsep=0pt]
            \item \textbf{Led the enhancement of IT infrastructure to increase operational efficiency by 30\%} by optimizing network performance and server management.
            \item \textbf{Directed the implementation of IT security protocols to reduce data breaches by 25\%} through the introduction of advanced encryption and monitoring tools.
            \item \textbf{Spearheaded the development of an advanced biopsychology and engineering curriculum, boosting student engagement by 40\%} as measured by increased student participation and feedback.
        \end{itemize}

    \item \textbf{Lead Systems Administrator, Dutchie}
        \hfill \textit{July 2021 – Nov 2022}
        \begin{itemize}[leftmargin=0.5cm, itemsep=0pt]
            \item \textbf{Managed and led a team responsible for maintaining systems for the entire support team, achieving 99.9\% system uptime} through proactive maintenance and monitoring.
            \item \textbf{Oversaw the resolution of technical issues to reduce downtime by 20\%} by implementing a new incident response strategy and improving system resilience.
            \item \textbf{Enhanced user experience by directing SaaS systems management and creating technical content, resulting in a 15\% increase in user satisfaction scores} from quarterly surveys.
        \end{itemize}

    \item \textbf{Aerospace Medicine, SpaceX}
        \hfill \textit{Aug 2020 – Jan 2021}
        \begin{itemize}[leftmargin=0.5cm, itemsep=0pt]
            \item \textbf{Led the COVID response team, implementing safety measures that reduced employee and crew cases by 50\%} as tracked by internal health records and weekly testing results.
            \item \textbf{Coordinated medical research efforts with academic and private organizations, contributing to five published papers in peer-reviewed journals} and enhancing the organization's research profile.
            \item \textbf{Supported flight surgeons and medical fellows in research projects, increasing team productivity by 30\%} through effective project management and resource allocation.
        \end{itemize}

    \item \textbf{Backend Team Lead Engineer, BayShield}
        \hfill \textit{Mar 2020 – Sep 2020}
        \begin{itemize}[leftmargin=0.5cm, itemsep=0pt]
            \item \textbf{Led a team of engineers to win the Jacobs prize at UC Berkeley, increasing project visibility by 50\%} through strategic presentations and stakeholder engagement.
            \item \textbf{Directed the engineering of an app supplying central California with PPE, achieving a 90\% distribution efficiency rate} as measured by delivery metrics and user feedback.
        \end{itemize}

    \item \textbf{Software Engineer, GitHub}
        \hfill \textit{May 2019 – Jan 2020}
        \begin{itemize}[leftmargin=0.5cm, itemsep=0pt]
            \item \textbf{Streamlined support operations by developing and maintaining internal tools, reducing response time by 25\%} as evidenced by support ticket resolution times and customer feedback.
            \item \textbf{Collaborated with cross-functional teams to improve product features, increasing customer satisfaction by 20\%} based on Net Promoter Scores (NPS) and user surveys.
            \item \textbf{Provided technical support and mentorship to junior engineers, enhancing their performance and contributing to a 15\% increase in team productivity} as measured by project completion rates and peer reviews.
        \end{itemize}
\end{itemize}

\section*{Academic Experience}
\begin{itemize}[leftmargin=0cm, itemsep=0pt]
    \item \textbf{Research Assistant, CameLAB, Connecticut College}
        \hfill \textit{Aug 2017 – May 2021}
        \begin{itemize}[leftmargin=0.5cm, itemsep=0pt]
            \item \textbf{Conducted experiments using 3D Reach Tracker, EEG, and eye-tracking technology, contributing to 10 published papers in high-impact journals}.
            \item \textbf{Analyzed data using Matlab, reducing analysis time by 20\%} through the development of automated processing scripts and workflows.
        \end{itemize}

    \item \textbf{Bioinformatics Researcher, Connecticut College}
        \hfill \textit{Jan 2020 – May 2021}
        \begin{itemize}[leftmargin=0.5cm, itemsep=0pt]
            \item \textbf{Created an Apache Spark pipeline to analyze single nucleotide polymorphisms, increasing processing speed by 30\%} compared to traditional methods.
            \item \textbf{Developed algorithms to analyze medical imaging from DICOM files, enhancing accuracy by 25\%} as validated by cross-referencing with manual analysis.
        \end{itemize}
\end{itemize}

\section*{Education}
\begin{itemize}[leftmargin=0cm, itemsep=0pt]
    \item \textbf{Bridges Graduate School of Cognitive Diversity in Education}
        \hfill \textit{Expected 2025}
        \begin{itemize}[leftmargin=0.5cm, itemsep=0pt]
            \item Master's in Cognitive Diversity in Education
        \end{itemize}
    \item \textbf{Connecticut College}
        \hfill \textit{Aug 2017 – May 2021}
        \begin{itemize}[leftmargin=0.5cm, itemsep=0pt]
            \item B.A. in Computer Science and Psychology
            \item Minor in Cognitive Science
            \item Certificate of Arts and Technology
        \end{itemize}
\end{itemize}

\end{document}
